---
title: "The gaussian LASSO without randomization"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The gaussian LASSO without randomization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6.5, fig.height = 4.2,
                      eval = requireNamespace("glmnet", quietly = TRUE))
has_pkg <- requireNamespace("glmnet", quietly = TRUE)
```

The polyhedral lemma of Lee et al. (2016) gives exact selective inference after the LASSO
fitted on all the data, with no randomization: conditionally on the selected variables and
their signs, each estimate is a truncated Gaussian. This vignette fits a gaussian LASSO with
`glmnet`, computes the selective intervals with `glmnet_inference()`, and checks their
calibration by simulation. `vignette("no_randomization")` does the same for a logistic
LASSO, and `vignette("gaussian_lasso")` adds randomization.

The targets are the coefficients of the selected model $E$: the population least squares
coefficients of $y$ on $X_E$ (and the intercept). The estimate is the least squares
coefficient on $X_E$; $\sigma^2$ is estimated from the full least squares fit.

```{r}
library(lassoinf)
n <- 200; p <- 20
beta <- c(0.5, 0.25, -0.25, rep(0, p - 3))
make_data <- function() {
  x <- matrix(rnorm(n * p), n, p)
  list(x = x, y = drop(x %*% beta) + rnorm(n))
}
set.seed(0)
d <- make_data()

lam <- 0.1
path <- lam * exp(seq(log(10), 0, length.out = 30))
fit <- glmnet::glmnet(d$x, d$y, lambda = path, control = list(thresh = 1e-14))
```

We fit a path ending at $\lambda$ with a small `thresh`, so that the solution satisfies the
KKT conditions closely.

## Inference

```{r}
li <- glmnet_inference(fit, d$x, d$y, s = lam, level = 0.9)
li$summary()
```

Index 0 is the intercept. `beta_hat` is the LASSO coefficient; the estimate of each target
is the least squares coefficient on the selected variables, shown in the naive (Wald)
intervals, which ignore the selection:

```{r}
li$`_naive`
```

The target for the selected model is $W (\hat{Q}\beta^*)_E$ with $W = \hat{Q}_{E,E}^{-1}$
and $\beta^* = (0, \beta)$:

```{r}
target <- function(li) drop(li$W %*% (li$Q_hat %*% c(0, beta))[li$E + 1])
```

## Calibration

The pivot of each target, the conditional CDF of its estimate at the true value, should be
uniform. We compute it from the same pieces `LassoInference` uses: the contrast, its
truncation interval and the truncated bivariate normal. Without randomization, the
randomization variance is a small 0.001 times $\text{Var}(Z)$.

```{r}
pivot <- function(li, j, truth) {
  contrast <- li$si$compute_contrast(li$contrasts[[as.character(j)]])
  interval <- contrast$get_interval(0, li$A, li$b)
  variance <- contrast$naive_variance
  tbn <- TruncBivariateNormal$new(a_coeff = contrast$bar_s^2 / variance, b_coeff = 1,
                                  L = interval[1], U = interval[2],
                                  sig_omega = contrast$bar_s, sig_x = sqrt(variance))
  tbn$cdf(theta = truth / variance, x = contrast$theta_hat)
}

one_replication <- function() {
  d <- make_data()
  fit <- glmnet::glmnet(d$x, d$y, lambda = path, control = list(thresh = 1e-14))
  li <- glmnet_inference(fit, d$x, d$y, s = lam, level = 0.9)
  s <- li$summary()
  keep <- s$index != 0                                # the selected variables, not the intercept
  if (!any(keep)) return(NULL)
  truth <- target(li)[keep]
  naive <- li$`_naive`[keep, ]
  naive_sd <- (naive$upper_conf - naive$lower_conf) / (2 * qnorm(0.95))
  data.frame(signal = beta[s$index[keep]] != 0,
             pivot = mapply(function(j, t) pivot(li, j, t), s$index[keep], truth),
             cover = s$lower_conf[keep] <= truth & truth <= s$upper_conf[keep],
             length = s$upper_conf[keep] - s$lower_conf[keep],
             naive_pivot = pnorm((naive$beta_hat - truth) / naive_sd),
             naive_cover = naive$lower_conf <= truth & truth <= naive$upper_conf,
             naive_length = naive$upper_conf - naive$lower_conf)
}

simulate <- function(nsim, seed = 1) {
  set.seed(seed)
  do.call(rbind, replicate(nsim, one_replication(), simplify = FALSE))
}
```

```{r, include = FALSE}
# The simulation results are saved in gaussian_lasso_polyhedral_sims.rds (simulate() sets
# its own seed, so they are the same). Set LASSOINF_RERUN_SIMS=true and rebuild the
# vignette to recompute them.
sims_file <- "gaussian_lasso_polyhedral_sims.rds"
if (!file.exists(sims_file) || identical(Sys.getenv("LASSOINF_RERUN_SIMS"), "true")) {
  saveRDS(simulate(nsim = 300), sims_file)
}
results <- readRDS(sims_file)
```

```{r, eval = if (has_pkg) -1 else FALSE}
results <- simulate(nsim = 300)
summarize <- function(r) {
  data.frame(variables = c(sum(r$signal), sum(!r$signal)),
             coverage = c(mean(r$cover[r$signal]), mean(r$cover[!r$signal])),
             naive_coverage = c(mean(r$naive_cover[r$signal]), mean(r$naive_cover[!r$signal])),
             median_length = c(median(r$length[r$signal]), median(r$length[!r$signal])),
             naive_median_length = c(median(r$naive_length[r$signal]), median(r$naive_length[!r$signal])),
             row.names = c("signal", "null"))
}
summarize(results)
```

```{r, include = FALSE}
ink <- "#0b0b0b"; ink2 <- "#52514e"; grid_col <- "#e5e4e0"
pal <- c("#2a78d6", "#eb6834")
pivot_plot <- function(pivots, labels, main) {
  op <- par(mar = c(4.2, 4.2, 2.2, 1), las = 1, col.axis = ink2, col.lab = ink2, fg = ink2)
  on.exit(par(op))
  plot(NA, xlim = c(0, 1), ylim = c(0, 1), xaxs = "i", yaxs = "i", bty = "n",
       xlab = "Uniform quantile", ylab = "Proportion of pivots below", main = main,
       col.main = ink, font.main = 1, cex.main = 1)
  abline(h = seq(0, 1, 0.25), v = seq(0, 1, 0.25), col = grid_col)
  abline(0, 1, lty = 2, col = ink2)
  xs <- seq(0, 1, length.out = 401)
  for (k in seq_along(pivots)) lines(xs, ecdf(pivots[[k]])(xs), col = pal[k], lwd = 2)
  legend("topleft", legend = labels, col = pal[seq_along(pivots)], lwd = 2, bty = "n",
         text.col = ink, inset = 0.02)
}
```

```{r, echo = FALSE, fig.alt = "Empirical CDFs of the polyhedral and naive pivots against the uniform; the polyhedral pivot follows the diagonal, the naive one does not."}
pivot_plot(list(results$pivot, results$naive_pivot),
           c("polyhedral (glmnet_inference)", "naive (ignores selection)"),
           "Pivots at the selected-model targets")
```

The polyhedral pivots follow the diagonal, and the intervals cover close to the nominal 90%
for signal and null variables alike. The naive intervals cover the selected null variables
far less often than 90%: those were selected because their estimates are large. The polyhedral intervals
are about as long as the naive ones for strong signals, and much longer for variables
selected near the selection boundary. Randomization gives shorter intervals there; see
`vignette("gaussian_lasso")`.

## Reference

Lee, J. D., Sun, D. L., Sun, Y. and Taylor, J. E. (2016). Exact post-selection inference,
with application to the lasso. *The Annals of Statistics*, 44(3), 907--927.
