---
title: "Inference after a glmnet fit: carving for logistic regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inference after a glmnet fit}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>",
                      eval = requireNamespace("glmnet", quietly = TRUE))
```

`glmnet_problem_from_fit` reads a fitted `glmnet` object and returns the LASSO problem it
solved, in the original coordinates: the solution, the gradient and Hessian of the smooth
part, the penalty weights and the bounds. These are the selection inputs of
`LassoInference`. This vignette uses them for **carving** in logistic regression. We select
variables with glmnet on a random half of the data, then do inference with all of it,
accounting for selection.

## Carving as randomization

glmnet divides the loss by the number of observations, and we use this per-observation scale
throughout. On the subsample of size $m = \pi n$, glmnet's problem gives the LASSO solution
$\hat{\beta}$, the gradient $G$ and the Hessian $\hat{Q}$ at $\hat{\beta}$. `LassoInference`
linearizes the selection with $\hat{Q}$, the information matrix at the fit on the model $E$,
and selects with

$$
Z + \omega = -G + \hat{Q}\hat{\beta} \approx \hat{Q}\tilde{\beta}_m,
$$

where $\tilde{\beta}_m$ is the unpenalized MLE on the subsample. The full-data statistic must use
the same matrix: $Z = \hat{Q}\bar{\beta}$, with $\bar{\beta}$ the unpenalized MLE on all the
data. With $I$ the per-observation Fisher information,
$\text{Var}(\bar{\beta}) \approx I^{-1}/n$ and $\tilde{\beta}_m - \bar{\beta}$ is asymptotically
independent of $\bar{\beta}$ with variance $I^{-1}(1/m - 1/n)$. So

$$
\Sigma = \text{Var}(Z) \approx \hat{Q} I^{-1} \hat{Q} / n, \qquad
\text{Var}(\omega) \approx \frac{1 - \pi}{\pi}\, \Sigma,
$$

and selecting on a subsample is randomized selection with `scalar_noise` $= (1 - \pi) / \pi$,
which is 1 for $\pi = 1/2$. We estimate $I$ by the information at $\bar{\beta}$.

## Data

```{r}
library(lassoinf)
set.seed(0)

n <- 600; p <- 30
beta <- c(0.6, -0.6, 0.4, rep(0, p - 3))
make_data <- function(n) {
  X <- matrix(rnorm(n * p), n, p)
  y <- rbinom(n, 1, plogis(drop(X %*% beta)))
  list(X = X, y = y)
}
d <- make_data(n)
```

## Select on half of the data with glmnet

We fit a path that ends at a fixed $\lambda$, with the default standardization and an
unpenalized intercept, and convert the fit at that $\lambda$ with `glmnet_problem_from_fit`. Its
coordinates are $(\text{intercept}, \beta)$, so index 0 is the intercept. The function warns if
the fit does not satisfy the KKT conditions closely enough, so a small `thresh` matters.

```{r}
pi_selection <- 0.5
lam <- 0.06
lambda_path <- lam * exp(seq(log(10), 0, length.out = 30))

select <- function(d) {
  sub <- sample(nrow(d$X), round(pi_selection * nrow(d$X)))
  fit <- glmnet::glmnet(d$X[sub, ], d$y[sub], family = "binomial",
                        lambda = lambda_path, control = list(thresh = 1e-14))
  prob <- glmnet_problem_from_fit(fit, d$X[sub, ], d$y[sub], s = lam)
  prob$sub <- sub
  prob
}
prob <- select(d)
which(prob$beta_hat[-1] != 0)
```

## Full-data score

The unpenalized fit on all the data gives $\bar{\beta}$ and the per-observation information
$I = X_1'WX_1 / n$ at $\bar{\beta}$, with $X_1 = [1, X]$.

```{r}
full_score <- function(d, Q_hat) {
  X1 <- cbind(1, d$X)
  bar_beta <- unname(coef(glm.fit(X1, d$y, family = binomial())))
  mu <- plogis(drop(X1 %*% bar_beta))
  I_full <- crossprod(X1, X1 * (mu * (1 - mu))) / nrow(X1)
  list(Z = drop(Q_hat %*% bar_beta), Sigma = Q_hat %*% solve(I_full, Q_hat) / nrow(X1))
}
full <- full_score(d, prob$Q_hat)
```

## Inference

```{r}
li <- LassoInference$new(prob$beta_hat, prob$G_hat, prob$Q_hat, prob$D, prob$L, prob$U,
                         full$Z, full$Sigma, NULL, (1 - pi_selection) / pi_selection,
                         level = 0.9)
summ <- li$summary()
summ$variable <- ifelse(summ$index == 0, "(Intercept)", paste0("x", summ$index))
summ
```

The estimate for the selected model is $W Z_E$, with $W = \hat{Q}_{E,E}^{-1}$, and its target is
$W (\hat{Q}\beta^*)_E$, with $\beta^* = (0, \beta)$ the true coefficients including the
intercept. When $E$ contains all the true signals, the target is $\beta^*_E$. Otherwise it is
the projection of $\beta^*$ onto the coordinates in $E$, in the metric given by the information
matrix $\hat{Q}$.

```{r}
target <- function(li) drop(li$W %*% (li$Q_hat %*% c(0, beta))[li$E + 1])
summ$truth <- target(li)
summ$cover <- summ$lower_conf <= summ$truth & summ$truth <= summ$upper_conf
summ[, c("variable", "lower_conf", "upper_conf", "p_value", "truth", "cover")]
```

For comparison, `li$"_naive"` holds Wald intervals that use all the data and ignore
selection. Data splitting refits the selected model on the half of the data not used for
selection:

```{r}
splitting <- function(d, prob, li, level = 0.9) {
  held_out <- setdiff(seq_len(nrow(d$X)), prob$sub)
  X1 <- cbind(1, d$X)[held_out, li$E + 1, drop = FALSE]
  fit <- glm.fit(X1, d$y[held_out], family = binomial())
  est <- unname(coef(fit))
  mu <- fit$fitted.values
  sd <- sqrt(diag(solve(crossprod(X1, X1 * (mu * (1 - mu))))))
  q <- qnorm(1 - (1 - level) / 2)
  data.frame(index = li$E, estimate = est, lower_conf = est - q * sd, upper_conf = est + q * sd)
}
li$`_naive`
splitting(d, prob, li)
```

The held-out refit targets the coefficients of the best-fitting logistic model on $X_E$. That
is the same as the target above when $E$ contains all the true signals.

## Coverage over repeated experiments

```{r}
one_replication <- function() {
  d <- make_data(n)
  prob <- select(d)
  full <- full_score(d, prob$Q_hat)
  li <- LassoInference$new(prob$beta_hat, prob$G_hat, prob$Q_hat, prob$D, prob$L, prob$U,
                           full$Z, full$Sigma, NULL, (1 - pi_selection) / pi_selection,
                           level = 0.9)
  summ <- li$summary()
  keep <- summ$index != 0   # report the selected variables, not the intercept
  truth <- target(li)[keep]
  covers <- function(df) (df$lower_conf <= truth & truth <= df$upper_conf)
  lengths <- function(df) df$upper_conf - df$lower_conf
  tabs <- list(carving = summ[keep, ], naive = li$`_naive`[keep, ],
               splitting = splitting(d, prob, li)[keep, ])
  data.frame(method = rep(names(tabs), each = sum(keep)),
             cover = unlist(lapply(tabs, covers)), length = unlist(lapply(tabs, lengths)),
             signal = rep(beta[summ$index[keep]] != 0, length(tabs)))
}

set.seed(1)
results <- do.call(rbind, replicate(100, one_replication(), simplify = FALSE))
data.frame(coverage = tapply(results$cover, results$method, mean),
           median_length = tapply(results$length, results$method, median))
```

Carving and data splitting both have close to the nominal 90% coverage. Carving also uses
the half of the data that selected the model, so its intervals are shorter. The naive
intervals ignore selection and undercover, almost entirely on the selected null variables.
Carving is a little below nominal on the true signals, which reflects the large-sample
approximations behind the Gaussian model for $(Z, \omega)$:

```{r}
with(results, tapply(cover, list(method, signal = signal), mean))
```
