---
title: "The leave-one-out uniLasso is a shifted uniLasso"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The leave-one-out uniLasso is a shifted uniLasso}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>",
                      eval = requireNamespace("uniLasso", quietly = TRUE))
has_pkg <- requireNamespace("uniLasso", quietly = TRUE)
```

By default, `uniLasso::uniLasso()` (`loo = TRUE`) fits its second-stage lasso to
*leave-one-out* univariate fits. With `loo = FALSE`, the uniLasso's penalty factors are
exactly $1/|\hat{\beta}^{\text{uni}}_j|$, and `unilasso_inference()` is exact
(`vignette("unilasso")`). This vignette shows that the two are closely related, which is
how `unilasso_inference()` handles `loo = TRUE` fits, approximately:

> The `loo = TRUE` solution at $\lambda$ solves, exactly, the `loo = FALSE` problem with
> $n\lambda$ replaced by $n\lambda + \kappa_j$ for feature $j$, with $\kappa_j$ explicit.
> Under local alternatives, $\kappa_j = 2\sigma^2 + O_p(n^{-1/2})$.

So the leave-one-out uniLasso is, to first order, the plain uniLasso at the larger
penalty $\lambda + 2\sigma^2/n$. The 2 is the trace of each univariate hat matrix (an
intercept and a slope). The same shift explains the sparsity of uniReg with leave-one-out
fits, and the correlation threshold Chatterjee, Hastie and Tibshirani (2025) observe in
their Section 4.

## Setup

Data are $(x_i, y_i)$, $i = 1, \dots, n$, with $x_i \in \mathbb{R}^p$. Write
$P = I - \mathbf{1}\mathbf{1}'/n$, $\tilde{y} = Py$, and $c_j = P x_j$ for the centered
$j$-th feature, with $S_j = c_j' c_j$ and $C = [c_1, \dots, c_p]$.

**Univariate fits.** The univariate regression of $y$ on $x_j$, with an intercept, has
slope $b_j = c_j'\tilde{y} / S_j$, fitted values $\eta_j = \bar{y}\mathbf{1} + b_j c_j$ and
residuals $r_j = y - \eta_j$. Its hat matrix and leverages are

$$
H_j = \frac{\mathbf{1}\mathbf{1}'}{n} + \frac{c_j c_j'}{S_j}, \qquad
h_{ij} = \frac{1}{n} + \frac{c_{ij}^2}{S_j}, \qquad
\sum_{i=1}^n h_{ij} = \text{tr}(H_j) = 2.
$$

**Leave-one-out fits.** The classical identity
$y_i - \eta_{ij}^{(-i)} = r_{ij} / (1 - h_{ij})$ gives the leave-one-out fitted values

$$
F_j = \eta_j + \delta_j, \qquad \delta_{ij} = -\frac{h_{ij}}{1 - h_{ij}}\, r_{ij}.
$$

**The two uniLassos.** With $B = \text{diag}(b_1, \dots, b_p)$, the uniLasso fits, for
features $G = [g_1, \dots, g_p]$,

$$
\hat{\theta} = \text{argmin}_{\theta_0, \theta \geq 0} \ \frac{1}{2n}\|y - \theta_0 \mathbf{1} - G\theta\|_2^2 + \lambda \sum_j \theta_j,
\qquad \hat{\beta} = B\hat{\theta},
$$

with $G = F$ for `loo = TRUE` and $G = \eta$ for `loo = FALSE`. (This is glmnet's scaling of
the loss, which the package uses; the paper writes $\frac{1}{n}$.) Profiling out
$\theta_0$, the KKT conditions are

$$
\tilde{g}_j' \big(\tilde{y} - \tilde{G}\hat{\theta}\big) \leq n\lambda, \quad \text{with equality if } \hat{\theta}_j > 0,
\qquad \tilde{G} = PG. \tag{KKT}
$$

For `loo = FALSE`, $P\eta = CB$. With $r = \tilde{y} - C\hat{\beta}$, (KKT) reads
$b_j c_j' r \leq n\lambda$. Dividing by $|b_j|$, with $s_j = \text{sign}(b_j)$,

$$
s_j c_j' r \leq \frac{n\lambda}{|b_j|}, \quad \text{with equality if } \hat{\beta}_j \neq 0, \qquad \text{sign}(\hat{\beta}_j) \in \{0, s_j\}.
$$

These are the KKT conditions of the lasso with penalty factors $1/|b_j|$ and the sign
constraints, in the score coordinates $Z = C'\tilde{y}$, $Q = C'C$ of this package:
$c_j' r = Z_j - (Q\hat{\beta})_j$ and $D_j = n\lambda / |b_j|$. This is the paper's
Proposition 1.

## An exact identity

Write $\Delta = [\delta_1, \dots, \delta_p]$, $\tilde{\delta}_j = P\delta_j$ and
$\tilde{\Delta} = P\Delta$.

**Lemma.** Let $\hat{\theta}$ solve the `loo = TRUE` problem, $\hat{\beta} = B\hat{\theta}$ and
$r = \tilde{y} - C\hat{\beta}$. Then for every $j$,

$$
b_j c_j' r \leq n\lambda + \kappa_j, \quad \text{with equality if } \hat{\theta}_j > 0,
$$

where

$$
\kappa_j = \underbrace{\sum_{i=1}^n \frac{h_{ij}}{1 - h_{ij}}\, r_{ij}\, r_i}_{A_j}
\;+\; \underbrace{b_j\, c_j' \tilde{\Delta} \hat{\theta}}_{B_j}
\;+\; \underbrace{\tilde{\delta}_j' \tilde{\Delta} \hat{\theta}}_{C_j}.
$$

So $\hat{\beta}$ satisfies the KKT conditions, and hence (by convexity) solves the
`loo = FALSE` uniLasso with the feature-specific penalties
$D_j = (n\lambda + \kappa_j)/|b_j|$, provided $n\lambda + \kappa_j \geq 0$.

*Proof.* Since $PF = P\eta + P\Delta = CB + \tilde{\Delta}$,

$$
\tilde{y} - \tilde{F}\hat{\theta} = \tilde{y} - C\hat{\beta} - \tilde{\Delta}\hat{\theta} = r - \tilde{\Delta}\hat{\theta},
$$

and therefore

$$
\tilde{F}_j'\big(\tilde{y} - \tilde{F}\hat{\theta}\big)
= (b_j c_j + \tilde{\delta}_j)'(r - \tilde{\Delta}\hat{\theta})
= b_j c_j' r + \tilde{\delta}_j' r - b_j c_j'\tilde{\Delta}\hat{\theta} - \tilde{\delta}_j'\tilde{\Delta}\hat{\theta}.
$$

Since $r$ is centered, $\tilde{\delta}_j' r = \delta_j' r = -A_j$, so the right side is
$b_j c_j' r - \kappa_j$. Substituting into (KKT) for $G = F$ gives the claim. $\square$

Nothing here is asymptotic. Since $\kappa_j$ depends on $\hat{\beta}$, the lemma is a
fixed-point characterization; but $\kappa_j$ is computable from the data and the fit.

## The size of $\kappa_j$

The shift matters in the regime where selection is not trivial. Under local alternatives
$\beta^* = \bar{\beta}/\sqrt{n}$, the slopes are $b_j = O_p(n^{-1/2})$, so the left side of
the KKT conditions, $b_j c_j' r$, is $O_p(1)$. The interesting $\lambda$ therefore have
$n\lambda = O(1)$, the same order as $\kappa_j$. The shift does not wash out as $n$ grows.

**Proposition.** Suppose

1. $p$ is fixed; the rows $x_i$ are i.i.d. with finite eighth moments and a positive
   definite covariance;
2. $y_i = \beta_0 + x_i'\beta^* + \varepsilon_i$ with $\varepsilon_i$ i.i.d., independent of
   $X$, with mean 0, variance $\sigma^2$ and a finite fourth moment;
3. $\beta^* = \bar{\beta}/\sqrt{n}$ for a fixed $\bar{\beta}$;
4. $n\lambda = O(1)$ and $\hat{\theta} = O_p(1)$.

Then for each $j$,

$$
\kappa_j = 2\sigma^2 + O_p(n^{-1/2}),
\qquad A_j = 2\sigma^2 + O_p(n^{-1/2}),
\qquad B_j = O_p(n^{-1}),
\qquad C_j = O_p(n^{-1}).
$$

If moreover $x_i$ and $\varepsilon_i$ are Gaussian, then
$\sqrt{n}\,\big(A_j/(2\sigma^2) - 1\big) \to N(0, 3)$.

*Proof.* Write $\tilde{\varepsilon} = P\varepsilon$. Under (3), the univariate residual is
$r_{ij} = \tilde{\varepsilon}_i + \rho_{ij}$ with $\rho_{ij} = c_i'\beta^* - b_j c_{ij}$, and the
uniLasso residual is $r_i = \tilde{\varepsilon}_i + \rho_i$ with
$\rho_i = c_i'(\beta^* - \hat{\beta})$. Here $c_i$ is the $i$-th row of $C$. Both
$\beta^*$ and $\hat{\beta} = B\hat{\theta}$ are $O_p(n^{-1/2})$, so
$|\rho_{ij}|, |\rho_i| \leq O_p(n^{-1/2})(1 + \|x_i\|)$. The leverages satisfy
$\sum_i h_{ij} = 2$, $\sum_i h_{ij}^2 = O_p(n^{-1})$, $\sum_i h_{ij}^4 = O_p(n^{-3})$ and
$\max_i h_{ij} = o_p(1)$, by (1).

*$A_j$.* Expand $r_{ij} r_i = \tilde{\varepsilon}_i^2 + \tilde{\varepsilon}_i(\rho_{ij} + \rho_i) + \rho_{ij}\rho_i$:

* $\sum_i h_{ij}\tilde{\varepsilon}_i^2 = \sigma^2 \sum_i h_{ij} + \sum_i h_{ij}(\varepsilon_i^2 - \sigma^2) + O_p(n^{-1})
  = 2\sigma^2 + O_p\big((\sum_i h_{ij}^2)^{1/2}\big) = 2\sigma^2 + O_p(n^{-1/2})$. The middle
  sum has mean zero given $X$ and variance $\text{Var}(\varepsilon^2)\sum_i h_{ij}^2$, and the
  $O_p(n^{-1})$ collects the terms in $\bar{\varepsilon}$.
* By Cauchy–Schwarz,
  $|\sum_i h_{ij}\tilde{\varepsilon}_i(\rho_{ij} + \rho_i)| \leq (\sum_i h_{ij}\tilde{\varepsilon}_i^2)^{1/2}(\sum_i h_{ij}(\rho_{ij} + \rho_i)^2)^{1/2} = O_p(1)\, O_p(n^{-1/2})$,
  and $\sum_i h_{ij}\rho_{ij}\rho_i = O_p(n^{-1})$.
* The factor $1/(1 - h_{ij}) = 1 + h_{ij}/(1 - h_{ij})$ adds at most
  $(1 - \max_i h_{ij})^{-1}(\sum_i h_{ij}^4)^{1/2}(\sum_i r_{ij}^2 r_i^2)^{1/2} = O_p(n^{-3/2})\,O_p(n^{1/2}) = O_p(n^{-1})$.

*$B_j$.* For each $k$, $c_j'\delta_k = -\sum_i c_{ij} h_{ik} r_{ik}/(1 - h_{ik})$. Its leading
part is $-\frac{1}{n} c_j' r_k - \frac{1}{S_k}\sum_i c_{ij} c_{ik}^2 r_{ik}$. Both
$c_j' r_k = c_j'(I - H_k)\tilde{y}$ and $\sum_i c_{ij} c_{ik}^2 r_{ik}$ are $O_p(\sqrt{n})$: their
$\tilde{\varepsilon}$ parts have mean zero and variance $O(n)$, and their $\rho$ parts are
$n \cdot O_p(n^{-1/2})$. With $S_k \asymp n$, $c_j'\delta_k = O_p(n^{-1/2})$. Hence
$c_j'\tilde{\Delta}\hat{\theta} = \sum_k \hat{\theta}_k c_j'\delta_k = O_p(n^{-1/2})$ by (4), and
$B_j = b_j\, O_p(n^{-1/2}) = O_p(n^{-1})$.

*$C_j$.* $|\tilde{\delta}_j'\tilde{\delta}_k| \leq \|\delta_j\|\,\|\delta_k\|$ and
$\|\delta_j\|^2 = \sum_i h_{ij}^2 r_{ij}^2/(1 - h_{ij})^2 = O_p(n \cdot n^{-2}) = O_p(n^{-1})$, so
$C_j = \sum_k \hat{\theta}_k \tilde{\delta}_j'\tilde{\delta}_k = O_p(n^{-1})$.

*The Gaussian constant.* The fluctuation of $A_j$ is that of
$\sum_i h_{ij}(\varepsilon_i^2 - \sigma^2)$, with variance $2\sigma^4\sum_i h_{ij}^2$. For
Gaussian $x$, $E c_{ij}^4 = 3 (E c_{ij}^2)^2$, so
$\sum_i h_{ij}^2 = \sum_i (1/n + c_{ij}^2/S_j)^2 = (1 + 2 + 3 + o_p(1))/n = (6 + o_p(1))/n$. The
variance of $A_j/(2\sigma^2)$ is then $3/n$, and a Lindeberg CLT given $X$ gives the limit.
$\square$

With $\hat{\sigma}^2$ the residual variance of the full least squares fit,
$2\hat{\sigma}^2 = (2/n)\sum_i \varepsilon_i^2 + O_p(n^{-1})$. So
$\kappa_j - 2\hat{\sigma}^2 = \sum_i (h_{ij} - 2/n)(\varepsilon_i^2 - \sigma^2) + O_p(n^{-1})$,
whose standard deviation in the Gaussian case is
$\sigma^2 \sqrt{2\sum_i (h_{ij} - 2/n)^2} = 2\sigma^2/\sqrt{n}$. The plug-in shift is accurate
to the same order as the true one.

## Consequences

**The penalty factors.** The `loo = TRUE` uniLasso at $\lambda$ is the `loo = FALSE`
uniLasso with penalties

$$
D_j = \frac{n\lambda + 2\sigma^2}{|b_j|}\big(1 + O_p(n^{-1/2})\big),
$$

the relative error being uniform in $b_j$, since it is $(\kappa_j - 2\sigma^2)/(n\lambda + 2\sigma^2)$.
In glmnet's units, $\lambda$ is replaced by $\lambda + 2\sigma^2/n$.

**uniReg.** With $\lambda = 0$, `uniReg(loo = TRUE)` is to first order the uniLasso with
$n\lambda = 2\sigma^2$, not sign-constrained least squares. The implicit penalty
$2\sigma^2/|b_j|$ is part of why it is so sparse. It also biases its coefficients toward
zero, which is why the bootstrap intervals of `ci.uniReg()` undercover the nonzero
coefficients (`vignette("unireg")`).

**The correlation threshold.** At $\hat{\theta} = 0$, the lemma with $r = \tilde{y}$ gives
$\tilde{F}_j'\tilde{y} = b_j c_j'\tilde{y} - A_j \approx S_j b_j^2 - 2\sigma^2$. The
leave-one-out feature is positively correlated with $y$ only if
$\text{cor}(x_j, y)^2\,\|\tilde{y}\|^2 > 2\sigma^2$, that is
$|\text{cor}(x_j, y)| \gtrsim \sqrt{2\sigma^2 / \|\tilde{y}\|^2} \approx \sqrt{2/n}$ when most of
the variance of $y$ is noise. For $n = 300$ that is $0.082$: the paper's "larger than about
0.08" (Section 4).

**Without an intercept** in the univariate fits, $\text{tr}(H_j) = 1$ and the shift is
$\sigma^2$.

## Numerical checks

### The identity

The leave-one-out features of `uniLasso::uniInfo()` match the closed form, and a
`loo = TRUE` fit satisfies the lemma to the solver's tolerance:

```{r}
library(lassoinf)
set.seed(1)
n <- 200; p <- 8
x <- matrix(rnorm(n * p), n, p) %*% chol(0.5 * diag(p) + 0.5)
y <- drop(x %*% c(0.3, -0.2, 0.15, rep(0, p - 3))) + rnorm(n)

loo_pieces <- function(x, y) {
  n <- nrow(x)
  C <- sweep(x, 2, colMeans(x))
  S <- colSums(C^2)
  b <- drop(crossprod(C, y - mean(y))) / S
  eta <- mean(y) + sweep(C, 2, b, "*")
  h <- 1 / n + sweep(C^2, 2, S, "/")
  list(C = C, b = b, h = h, eta = eta, delta = -h / (1 - h) * (y - eta))
}
lp <- loo_pieces(x, y)
info <- uniLasso::uniInfo(x, y, "gaussian", NULL, nit = 2, loo = TRUE, ridge = 0, eps = 1e-6)
c(max_abs_F_difference = max(abs(info$F - (lp$eta + lp$delta))),
  trace_H = unique(round(colSums(lp$h), 12)))

kappa_terms <- function(lp, y, beta) {
  theta <- beta / lp$b
  r <- (y - mean(y)) - drop(lp$C %*% beta)
  Dt <- sweep(lp$delta, 2, colMeans(lp$delta))
  list(r = r, A = -drop(crossprod(Dt, r)), B = lp$b * drop(crossprod(lp$C, Dt %*% theta)),
       C = drop(crossprod(Dt, Dt %*% theta)))
}
fit <- uniLasso::uniLasso(x, y, control = list(thresh = 1e-16))     # loo = TRUE
k <- 15
beta_hat <- as.numeric(fit$beta[, k])
kt <- kappa_terms(lp, y, beta_hat)
kappa <- kt$A + kt$B + kt$C
lhs <- lp$b * drop(crossprod(lp$C, kt$r))                          # b_j c_j' r
active <- beta_hat != 0
c(active_max_error = max(abs(lhs[active] - n * fit$lambda[k] - kappa[active])),
  inactive_max_violation = max(pmax(lhs[!active] - n * fit$lambda[k] - kappa[!active], 0)))
sigma2_hat <- sum(resid(lm(y ~ x))^2) / (n - p - 1)
round(kappa / (2 * sigma2_hat), 3)
```

### The rates

Over repeated draws under local alternatives, with $n\lambda = 1$ and $\sigma^2 = 1$:

```{r}
bbar <- c(3, -2, 1.5, rep(0, p - 3))
rates <- function(n, nsim = 60) {
  out <- replicate(nsim, {
    x <- matrix(rnorm(n * p), n, p) %*% chol(0.5 * diag(p) + 0.5)
    y <- drop(x %*% (bbar / sqrt(n))) + rnorm(n)
    lp <- loo_pieces(x, y)
    lam <- 1 / n
    fit <- uniLasso::uniLasso(x, y, lambda = lam * exp(seq(log(30), 0, length.out = 25)),
                              control = list(thresh = 1e-14))
    kt <- kappa_terms(lp, y, as.numeric(fit$beta[, 25]))
    sigma2_hat <- sum(resid(lm(y ~ x))^2) / (n - p - 1)
    rbind(A = kt$A / 2, B = kt$B, C = kt$C, plug_in = (kt$A + kt$B + kt$C - 2 * sigma2_hat) / 2)
  }, simplify = "array")
  data.frame(n = n,
             mean_A = mean(out["A", , ]),
             sqrt_n_sd_A = sqrt(n) * sd(out["A", , ]),
             n_median_abs_B = n * median(abs(out["B", , ])),
             n_median_abs_C = n * median(abs(out["C", , ])),
             sqrt_n_sd_plug_in = sqrt(n) * sd(out["plug_in", , ]))
}
```

```{r, include = FALSE}
# The simulation results are saved in unilasso_loo_sims.rds. Set LASSOINF_RERUN_SIMS=true
# and rebuild the vignette to recompute them.
sims_file <- "unilasso_loo_sims.rds"
rerun <- !file.exists(sims_file) || identical(Sys.getenv("LASSOINF_RERUN_SIMS"), "true")
if (rerun) {
  set.seed(2)
  rate_table <- do.call(rbind, lapply(c(100, 400, 1600, 6400), rates))
} else {
  sims <- readRDS(sims_file)
  rate_table <- sims$rates
}
```

```{r, eval = if (has_pkg) -(1:2) else FALSE}
set.seed(2)
rate_table <- do.call(rbind, lapply(c(100, 400, 1600, 6400), rates))
rate_table
```

`mean_A` is $A_j/(2\sigma^2)$, which tends to 1. `sqrt_n_sd_A` is stable near
$\sqrt{3} \approx 1.73$, the Gaussian constant of the proposition. `n_median_abs_B` and
`n_median_abs_C` are stable, so $B_j$ and $C_j$ are $O_p(n^{-1})$. `sqrt_n_sd_plug_in` is
$\sqrt{n}$ times the standard deviation of $(\kappa_j - 2\hat{\sigma}^2)/2$, near 1 as derived
above.

### The selections

A `loo = TRUE` fit at $\lambda$ against the `loo = FALSE` uniLasso at $\lambda$ and at
$\lambda + 2\hat{\sigma}^2/n$: how often do they select the same variables with the same
signs?

```{r}
agreement <- function(n, nsim = 40) {
  beta <- c(0.5, -0.4, 0.3, rep(0, p - 3)) * sqrt(200 / n) * 1.5
  same <- replicate(nsim, {
    x <- matrix(rnorm(n * p), n, p) %*% chol(0.5 * diag(p) + 0.5)
    y <- drop(x %*% beta) + rnorm(n)
    fit <- uniLasso::uniLasso(x, y)
    C <- sweep(x, 2, colMeans(x)); Q <- crossprod(C); Z <- drop(crossprod(C, y - mean(y)))
    sigma2_hat <- sum(resid(lm(y ~ x))^2) / (n - p - 1)
    sapply(round(length(fit$lambda) * c(0.3, 0.5)), function(k) {
      b <- sign(as.numeric(fit$beta[, k]))
      c(at_lambda = identical(b, sign(round(unilasso_fit(Q, Z, n * fit$lambda[k]), 10))),
        shifted = identical(b, sign(round(unilasso_fit(Q, Z, n * fit$lambda[k] + 2 * sigma2_hat), 10))))
    })
  })
  data.frame(n = n, fits = 2 * nsim, same_at_lambda = sum(same["at_lambda", , ]),
             same_shifted = sum(same["shifted", , ]))
}
```

```{r, include = FALSE}
if (rerun) {
  set.seed(3)
  agreement_table <- do.call(rbind, lapply(c(200, 1000, 5000), agreement))
} else {
  agreement_table <- sims$agreement
}
```

```{r, eval = if (has_pkg) -(1:2) else FALSE}
set.seed(3)
agreement_table <- do.call(rbind, lapply(c(200, 1000, 5000), agreement))
agreement_table
```

### Inference

What does this mean for inference? `unilasso_inference()` accepts `loo = TRUE` fits: it
computes $\kappa_j$ and treats the fit as the `loo = FALSE` uniLasso with penalties
$(n\lambda + \kappa_j)/|b_j|$, which the fit solves exactly. It warns that the result is
approximate, because $\kappa_j$ depends on the data and the inference treats it as fixed.
We compare its calibration for the full-model coefficients with the same inference at the
cruder shift $n\lambda + 2\hat{\sigma}^2$, and at the unshifted $n\lambda$.

```{r}
loo_calibration <- function(n, penalty, nsim_targets = 300) {
  beta <- c(0.5, -0.4, 0.3, 0, 0, 0) * sqrt(200 / n)
  q <- length(beta)
  pivots <- c(); cover <- c()
  while (length(pivots) < nsim_targets) {
    x <- matrix(rnorm(n * q), n, q) %*% chol(0.5 * diag(q) + 0.5)
    y <- drop(x %*% beta) + rnorm(n)
    fit <- uniLasso::uniLasso(x, y)                    # loo = TRUE
    k <- round(length(fit$lambda) * 0.4)
    b <- as.numeric(fit$beta[, k])
    if (all(b == 0)) next
    if (penalty == "n lambda + kappa_j") {
      ui <- suppressWarnings(unilasso_inference(fit, x, y, s = fit$lambda[k], level = 0.9))
    } else {
      C <- sweep(x, 2, colMeans(x)); Q <- crossprod(C); Z <- drop(crossprod(C, y - mean(y)))
      sigma2_hat <- sum(resid(lm(y ~ x))^2) / (n - q - 1)
      lam_Z <- n * fit$lambda[k] + if (penalty == "n lambda + 2 sigma2_hat") 2 * sigma2_hat else 0
      ui <- UniLassoInference$new(b, Z, Q, lam = lam_Z, Z_full = Z, Sigma = sigma2_hat * Q,
                                  scalar_noise = 0, level = 0.9)
    }
    for (j in ui$E) {
      r <- ui$results[[as.character(j)]]
      pivots <- c(pivots, ui$pivot(j, beta[j + 1]))
      cover <- c(cover, r$lower_conf <= beta[j + 1] && beta[j + 1] <= r$upper_conf)
    }
  }
  data.frame(n = n, penalty = penalty, targets = length(pivots),
             ks_p_value = suppressWarnings(ks.test(pivots, "punif")$p.value),
             coverage = mean(cover))
}
penalties <- c("n lambda + kappa_j", "n lambda + 2 sigma2_hat", "n lambda")
```

```{r, include = FALSE}
if (rerun) {
  set.seed(4)
  calibration_table <- do.call(rbind, lapply(c(100, 200, 1000), function(n)
    do.call(rbind, lapply(penalties, function(pen) loo_calibration(n, pen)))))
  saveRDS(list(rates = rate_table, agreement = agreement_table,
               calibration = calibration_table), sims_file)
} else {
  calibration_table <- sims$calibration
}
```

```{r, eval = if (has_pkg) -(1:2) else FALSE}
set.seed(4)
calibration_table <- do.call(rbind, lapply(c(100, 200, 1000), function(n)
  do.call(rbind, lapply(penalties, function(pen) loo_calibration(n, pen)))))
calibration_table
```

At the unshifted $\lambda$ the pivots are far from uniform and the 90% intervals cover
little more than half the time. Both shifts restore approximate calibration. The exact
$\kappa_j$ does better than $2\hat{\sigma}^2$, most of all at small $n$. With it, the fit
satisfies the KKT conditions of the shifted problem to the solver's tolerance, so the
one-step adjustment in `UniLassoInference` changes nothing and the estimates are exactly
the full-model least squares coefficients. With $2\hat{\sigma}^2$, the fit satisfies them
only to $O_p(n^{-1/2})$, and the adjustment moves the estimates. In both cases the
remaining approximation is that the shift is treated as fixed, though it depends on the
data.

The proposition assumes local alternatives, $b_j = O_p(n^{-1/2})$ with $\hat{\theta}$ of
moderate size. A strong feature, with $\sqrt{n}|b_j|$ large, can have a $B_j$ that is not
small, particularly when a correlated weak feature has a large $\hat{\theta}_k$. At
$n = 100$ in this design, $n\lambda + \kappa_j$ was occasionally negative for such a
feature. The lemma holds regardless, so `unilasso_inference()` uses the exact $\kappa_j$
whatever their size; only the $2\hat{\sigma}^2$ approximation breaks down there.

## Reference

Chatterjee, S., Hastie, T. and Tibshirani, R. (2025). Univariate-guided sparse regression.
*arXiv preprint*. doi:10.48550/arXiv.2501.18360
