---
title: "Inference after uniReg, compared with the bootstrap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inference after uniReg, compared with the bootstrap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6.5, fig.height = 4.6,
                      eval = requireNamespace("uniLasso", quietly = TRUE))
has_pkg <- requireNamespace("uniLasso", quietly = TRUE)
```

uniReg (Chatterjee, Hastie and Tibshirani, 2025) is the unpenalized uniLasso: least
squares with the signs constrained to those of the univariate regressions,

$$
\min_{\beta_0, \beta} \ \frac{1}{2n}\|y - \beta_0 - X\beta\|_2^2
\quad \text{subject to} \quad \text{sign}(\beta_j) \in \{0, \text{sign}(\hat{\beta}^{\text{uni}}_j)\},
$$

where $\hat{\beta}^{\text{uni}}_j$ is the slope of the univariate regression of $y$ on $x_j$.
The sign constraints set some coefficients to zero, so uniReg selects variables.
`uniLasso::uniReg(loo = FALSE)` solves this problem.

The uniLasso package offers `ci.uniReg()`: percentile bootstrap intervals for each
coefficient, from refitting uniReg to resampled data. `unilasso_inference()` instead gives
selective intervals for the full-model coefficients of the variables uniReg selects. These
condition on the selection and on the signs of the univariate coefficients, and are exact in
the Gaussian linear model; see `vignette("unilasso")`. This vignette compares the two.

```{r}
library(lassoinf)
n <- 200; p <- 8
beta <- 0.18 * c(1, -0.8, 0.6, rep(0, p - 3))
make_data <- function() {
  x <- matrix(rnorm(n * p), n, p) %*% chol(0.5 * diag(p) + 0.5)
  list(x = x, y = drop(x %*% beta) + rnorm(n))
}
set.seed(0)
d <- make_data()
```

## One data set

```{r}
reg <- uniLasso::uniReg(d$x, d$y, loo = FALSE, control = list(thresh = 1e-14))
unilasso_inference(reg, d$x, d$y, level = 0.9)$summary()
```

`ci.uniReg()` passes its extra arguments to `uniReg()`. Its default, like uniReg's, is
`loo = TRUE`, which regresses $y$ on leave-one-out univariate fits:

```{r}
set.seed(1)
uniLasso::ci.uniReg(d$x, d$y, B = 200, alpha = 0.1)
```

## Coverage

In each replication we compute three sets of 90% intervals for the true coefficients:

* `unilasso_inference()` after `uniReg(loo = FALSE)`, for the selected variables;
* `ci.uniReg()` with its default `loo = TRUE`, for every variable;
* `ci.uniReg(loo = FALSE)`, for every variable.

For the bootstrap we report coverage over all replications and also when its own fit
selected the variable (a nonzero coefficient), the event the selective intervals condition
on.

```{r}
one_replication <- function(B = 200) {
  d <- make_data()
  reg <- uniLasso::uniReg(d$x, d$y, loo = FALSE, control = list(thresh = 1e-14))
  ui <- unilasso_inference(reg, d$x, d$y, level = 0.9)
  boot <- list(default = uniLasso::ci.uniReg(d$x, d$y, B = B, alpha = 0.1),
               loo_false = uniLasso::ci.uniReg(d$x, d$y, B = B, alpha = 0.1, loo = FALSE,
                                               control = list(thresh = 1e-14)))
  rows <- list()
  for (j in seq_len(p)) {
    r <- ui$results[[as.character(j - 1)]]
    if (!is.null(r)) {
      rows[[length(rows) + 1]] <- data.frame(method = "selective", variable = j, selected = TRUE,
        cover = r$lower_conf <= beta[j] && beta[j] <= r$upper_conf, length = r$upper_conf - r$lower_conf)
    }
    for (b in names(boot)) {
      ci <- boot[[b]]
      rows[[length(rows) + 1]] <- data.frame(method = paste0("ci.uniReg (", b, ")"), variable = j,
        selected = ci[j, 1] != 0, cover = ci[j, 2] <= beta[j] && beta[j] <= ci[j, 3],
        length = ci[j, 3] - ci[j, 2])
    }
  }
  do.call(rbind, rows)
}

simulate <- function(nsim, seed = 1) {
  set.seed(seed)
  do.call(rbind, replicate(nsim, one_replication(), simplify = FALSE))
}
```

```{r, include = FALSE}
# The simulations take several minutes, so their results are saved in unireg_sims.rds
# (simulate() sets its own seed, so they are the same). Set LASSOINF_RERUN_SIMS=true and
# rebuild the vignette to recompute them.
sims_file <- "unireg_sims.rds"
if (!file.exists(sims_file) || identical(Sys.getenv("LASSOINF_RERUN_SIMS"), "true")) {
  saveRDS(simulate(nsim = 150), sims_file)
}
results <- readRDS(sims_file)
```

```{r, eval = if (has_pkg) -1 else FALSE}
results <- simulate(nsim = 150)
results$signal <- beta[results$variable] != 0
coverage_table <- function(r) {
  f <- function(x) round(mean(x), 3)
  do.call(rbind, lapply(split(r, r$method), function(m) data.frame(
    method = m$method[1],
    signal_all = f(m$cover[m$signal]), null_all = f(m$cover[!m$signal]),
    signal_selected = f(m$cover[m$signal & m$selected]), null_selected = f(m$cover[!m$signal & m$selected]),
    median_length = round(median(m$length[m$selected]), 3))))
}
coverage_table(results)
```

For the selective intervals "all" and "selected" are the same: they exist only for selected
variables. `median_length` is over selected variables.

```{r, include = FALSE}
ink <- "#0b0b0b"; ink2 <- "#52514e"; grid_col <- "#e5e4e0"
pal <- c("#2a78d6", "#eb6834", "#1baf7a")
coverage_plot <- function(cov, labels, nominal, main) {
  # cov: a matrix of coverages, variables in rows and methods in columns
  k <- ncol(cov); m <- nrow(cov)
  op <- par(mar = c(4.2, 7.5, 2.2, 1), las = 1, col.axis = ink2, col.lab = ink2, fg = ink2)
  on.exit(par(op))
  xlim <- c(min(0.25, floor(10 * min(cov, na.rm = TRUE)) / 10), 1)
  # rows 1..m, with space below the last row for the legend
  plot(NA, xlim = xlim, ylim = c(m + 0.5 + 0.55 * k, 0.4), yaxt = "n", bty = "n",
       xlab = "Coverage of 90% intervals", ylab = "", main = main, col.main = ink,
       font.main = 1, cex.main = 1)
  abline(v = seq(0, 1, 0.1), col = grid_col)
  abline(v = nominal, lty = 2, col = ink2)
  axis(2, at = seq_len(m), labels = rownames(cov), tick = FALSE, col.axis = ink)
  off <- seq(-0.22, 0.22, length.out = k)
  pch <- c(19, 17, 15)
  for (j in seq_len(k)) points(cov[, j], seq_len(m) + off[j], pch = pch[j], col = pal[j], cex = 1.3)
  legend("bottomleft", legend = labels, pch = pch[seq_len(k)], col = pal[seq_len(k)], bty = "n",
         text.col = ink, pt.cex = 1.3, inset = 0.02, bg = "white")
}
```

```{r, echo = FALSE, fig.alt = "Coverage of 90% intervals for each coefficient: selective intervals near 90% for all coefficients; the default ci.uniReg undercovers the three signals and overcovers the nulls."}
cov <- sapply(c("selective", "ci.uniReg (default)", "ci.uniReg (loo_false)"), function(meth) {
  m <- results[results$method == meth, ]
  tapply(m$cover, factor(m$variable, levels = seq_len(p)), mean)
})
rownames(cov) <- sprintf("x%d (%.3f)", seq_len(p), beta)
coverage_plot(cov, c("selective, when selected", "ci.uniReg, default (loo = TRUE)", "ci.uniReg, loo = FALSE"),
              0.9, "Coverage by coefficient (true value in parentheses)")
```

The selective intervals cover close to 90% for every coefficient, signal or null. With its
default `loo = TRUE`, `ci.uniReg()` undercovers the nonzero coefficients badly and covers the
zero ones essentially always. Leave-one-out fits shrink small univariate effects toward
zero, which acts like an extra penalty on every coefficient, so the bootstrap intervals are
centered on shrunken estimates. With `loo = FALSE` the bootstrap covers closer to nominal
here, though it is conservative for the null coefficients. The percentile bootstrap has no
guarantee for coefficients near the boundary that the sign constraints create.

The selective intervals are longer than the bootstrap ones (see `median_length`), most of all
for variables selected close to the selection boundary. That is the price of conditioning on
the selection. Randomized selection gives shorter intervals: `UniLassoInference$new()` with a
`scalar_noise` well above the 0.001 used without randomization, e.g. 1 (selection on about
half the information).

## References

Chatterjee, S., Hastie, T. and Tibshirani, R. (2025). Univariate-guided sparse regression.
*arXiv preprint*. doi:10.48550/arXiv.2501.18360
