---
title: "uniReg with and without leave-one-out"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{uniReg with and without leave-one-out}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6.5, fig.height = 3.6,
                      eval = requireNamespace("uniLasso", quietly = TRUE))
has_pkg <- requireNamespace("uniLasso", quietly = TRUE)
```

In `vignette("unireg")`, the bootstrap intervals of `uniLasso::ci.uniReg()` behave very
differently with and without leave-one-out fits. With the default `loo = TRUE` they cover
the weak nonzero coefficients poorly, and never when the univariate sign is wrong. With
`loo = FALSE` they do much better. Both versions constrain the coefficients to the same
signs, so why the difference? This vignette explains it. The short answer: with
leave-one-out fits, uniReg is not least squares with sign constraints. It is a uniLasso
with a penalty that grows as the univariate slope shrinks, and that penalty sets weak
coefficients to zero whatever their sign.

## Both versions use the same signs

uniReg fits $y$ on features built from the univariate regressions, with nonnegative
coefficients $\theta_j \geq 0$. It reports $\hat{\beta}_j = b_j \hat{\theta}_j$, where $b_j$ is
the slope of the univariate regression of $y$ on $x_j$. That holds with or without
leave-one-out:

* `loo = FALSE` uses the univariate fits $\eta_j = \bar{y} + b_j(x_j - \bar{x}_j)$ as features.
  This is least squares with the constraints $\text{sign}(\beta_j) \in \{0, \text{sign}(b_j)\}$.
* `loo = TRUE` uses their leave-one-out versions $F_j$.

Either way $\text{sign}(\hat{\beta}_j) \in \{0, \text{sign}(b_j)\}$. When a true coefficient is
small, of order $n^{-1/2}$, its univariate slope $b_j$ has the wrong sign with substantial
probability, and then both versions can only set it to zero or give it the wrong sign. The
two versions make the same sign errors.

## Leave-one-out acts as a penalty

`vignette("unilasso_loo")` shows that the leave-one-out uniLasso at $\lambda$ solves the
plain uniLasso with $n\lambda$ replaced by $n\lambda + 2\sigma^2$, to first order. The 2
is the trace of each univariate hat matrix. So uniReg with `loo = TRUE` ($\lambda = 0$) is
approximately the plain uniLasso with $n\lambda = 2\sigma^2$, with penalty factors
$2\sigma^2/|b_j|$.

The orthogonal case shows what this does. With centered, orthogonal features, the
uniLasso's KKT conditions $b_j c_j'(\tilde{y} - C\hat{\beta}) = n\lambda$ give
$b_j S_j (b_j - \hat{\beta}_j) = n\lambda$, so

$$
\hat{\beta}_j = b_j \left(1 - \frac{n\lambda}{S_j b_j^2}\right)_+
= b_j \left(1 - \frac{2}{t_j^2}\right)_+ \quad \text{for } n\lambda = 2\sigma^2,
$$

where $S_j = \|x_j - \bar{x}_j\|^2$ and $t_j = b_j \sqrt{S_j}/\sigma$ is the univariate
$t$-statistic. **uniReg with leave-one-out drops every feature with $|t_j| < \sqrt{2}$, and
shrinks the rest by the factor $1 - 2/t_j^2$.** A coefficient with $t_j = 2$ is halved.
Without leave-one-out, $\lambda = 0$ and there is no shrinkage at all.

A check, with orthogonal features and $\hat{\sigma}^2$ from the full least squares fit:

```{r}
set.seed(6)
n <- 400; p <- 10
x <- qr.Q(qr(scale(matrix(rnorm(n * p), n, p), scale = FALSE))) * sqrt(n)  # centered, orthogonal
y <- drop(x %*% (c(2.5, -2, 1.5, 1, rep(0, p - 4)) / sqrt(n))) + rnorm(n)
fit <- uniLasso::uniReg(x, y, control = list(thresh = 1e-14))           # loo = TRUE
S <- colSums(x^2)
b <- drop(crossprod(x, y - mean(y))) / S
sigma2_hat <- sum(resid(lm(y ~ x))^2) / (n - p - 1)
t <- b * sqrt(S / sigma2_hat)
round(rbind(t = t, uniReg_loo = as.numeric(fit$beta), formula = b * pmax(1 - 2 / t^2, 0),
            uniReg_no_loo = as.numeric(uniLasso::uniReg(x, y, loo = FALSE)$beta)), 4)
```

The formula matches up to the $O_p(n^{-1/2})$ error of the approximation. Features with
$|t_j| < \sqrt{2}$ are zero.

The shrinkage is of the same order as the standard error. A coefficient of size
$\beta_j = \bar{\beta}_j/\sqrt{n}$ has $t_j = O_p(1)$, so the shrinkage
$2 b_j / t_j^2$ is $O_p(n^{-1/2})$, like the noise in $\hat{\beta}_j$. It does not go away
as $n$ grows.

## What the bootstrap sees

`ci.uniReg()` refits uniReg to resampled data and reports the 5% and 95% quantiles of
the refitted coefficients. We repeat its bootstrap and keep the replicates. The design
is that of `vignette("unireg")`: correlation 0.5 between features and
$\beta = 0.18\,(1, -0.8, 0.6, 0, \dots, 0)$. There the marginal effect of $x_2$ is zero
($-0.8 + 0.5 \times (1 + 0.6) = 0$), so its univariate sign is close to a coin flip, while
$x_1$ has a marginal effect of $0.9 \times 0.18$.

```{r}
n <- 200; p <- 8
beta <- 0.18 * c(1, -0.8, 0.6, rep(0, p - 3))
make_data <- function() {
  x <- matrix(rnorm(n * p), n, p) %*% chol(0.5 * diag(p) + 0.5)
  list(x = x, y = drop(x %*% beta) + rnorm(n))
}

boot_coefs <- function(d, loo, B = 200) {
  replicate(B, {
    w <- tabulate(sample(nrow(d$x), replace = TRUE), nbins = nrow(d$x))
    as.numeric(coef(uniLasso::uniReg(d$x, d$y, weights = w, loo = loo,
                                     control = list(thresh = 1e-12))))[-1]
  })
}

one_replication <- function(B = 200) {
  d <- make_data()
  b_uni <- apply(d$x, 2, function(xj) cov(xj, d$y) / var(xj))
  do.call(rbind, lapply(c(TRUE, FALSE), function(loo) {
    draws <- boot_coefs(d, loo, B)
    fit <- as.numeric(coef(uniLasso::uniReg(d$x, d$y, loo = loo, control = list(thresh = 1e-12))))[-1]
    do.call(rbind, lapply(1:2, function(j) {
      q <- quantile(draws[j, ], c(0.05, 0.95))
      data.frame(coefficient = paste0("x", j), loo = loo,
                 univariate_sign = ifelse(sign(b_uni[j]) == sign(beta[j]), "right", "wrong"),
                 fit_is_zero = fit[j] == 0, boot_at_zero = mean(draws[j, ] == 0),
                 boot_on_true_side = mean(sign(draws[j, ]) == sign(beta[j])),
                 cover = q[1] <= beta[j] && beta[j] <= q[2])
    }))
  }))
}

simulate <- function(nsim, seed = 1) {
  set.seed(seed)
  do.call(rbind, replicate(nsim, one_replication(), simplify = FALSE))
}
```

```{r, include = FALSE}
# The simulations take a few minutes, so their results are saved in unireg_loo_sims.rds
# (simulate() sets its own seed, so they are the same). Set LASSOINF_RERUN_SIMS=true and
# rebuild the vignette to recompute them.
sims_file <- "unireg_loo_sims.rds"
if (!file.exists(sims_file) || identical(Sys.getenv("LASSOINF_RERUN_SIMS"), "true")) {
  saveRDS(simulate(nsim = 60), sims_file)
}
results <- readRDS(sims_file)
```

```{r, eval = if (has_pkg) -1 else FALSE}
results <- simulate(nsim = 60)
cols <- c("fit_is_zero", "boot_at_zero", "boot_on_true_side", "cover")
tab <- aggregate(results[cols], results[c("coefficient", "univariate_sign", "loo")], mean)
tab$cases <- aggregate(results["cover"], results[c("coefficient", "univariate_sign", "loo")], length)$cover
tab[cols] <- lapply(tab[cols], round, 2)
tab[order(tab$coefficient, tab$univariate_sign, !tab$loo), ]
```

The columns are the fraction of data sets in which uniReg's own fit is zero, and, averaged
over data sets, the fractions of bootstrap replicates that are zero and that are on the
true side of zero; `cover` is the coverage of the 90% percentile interval.

Three things happen.

1. **With leave-one-out, weak coefficients are zero in most fits and most replicates,
   whatever their sign.** The penalty $2\sigma^2/|b_j|$ is large exactly when $b_j$ is
   small. Even $x_1$, with the right sign, is often zero. A percentile interval from a
   bootstrap distribution with most of its mass at zero is close to $[0, 0]$, or reaches
   only a little way from zero toward the truth, so it misses the true value.
2. **Without leave-one-out there is no penalty.** A coefficient with the right univariate
   sign is estimated by sign-constrained least squares, unshrunk, and the bootstrap
   intervals cover close to nominal.
3. **When the univariate sign is wrong, the bootstrap without leave-one-out can still
   cover.** Here the marginal effect is near zero, so the univariate sign also flips
   across bootstrap samples. In the samples where it is right, the coefficient is free to
   take its unpenalized value on the true side, which spreads the bootstrap distribution
   across zero. With leave-one-out, the same samples have a small $|b_j^*|$ and hence a
   large penalty, and the coefficient stays at zero.

One data set where $x_2$'s univariate sign is wrong. The points are the 200 bootstrap
replicates of its coefficient (jittered vertically), and the bar under them is the 90%
percentile interval that `ci.uniReg()` would report. With leave-one-out, the bar is the
single point $[0, 0]$:

```{r, include = FALSE}
ink <- "#0b0b0b"; ink2 <- "#52514e"; grid_col <- "#e5e4e0"
pal <- c(loo = "#eb6834", no_loo = "#1baf7a")
replicate_plot <- function(draws, truth, labels, main) {
  op <- par(mar = c(4.2, 6.5, 2.2, 1), las = 1, col.axis = ink2, col.lab = ink2, fg = ink2)
  on.exit(par(op))
  xlim <- range(c(unlist(draws), truth, 0)) + c(-0.02, 0.02)
  plot(NA, xlim = xlim, ylim = c(0.4, length(draws) + 0.6), yaxt = "n", bty = "n",
       xlab = "Bootstrap replicate of the uniReg coefficient", ylab = "", main = main,
       col.main = ink, font.main = 1, cex.main = 1)
  abline(v = pretty(xlim), col = grid_col)
  abline(v = 0, col = ink2)
  abline(v = truth, lty = 2, col = ink)
  axis(2, at = seq_along(draws), labels = labels, tick = FALSE, col.axis = ink)
  for (k in seq_along(draws)) {
    points(draws[[k]], k + runif(length(draws[[k]]), -0.25, 0.25), pch = 19, cex = 0.7,
           col = adjustcolor(pal[k], 0.55))
    q <- quantile(draws[[k]], c(0.05, 0.95))
    segments(q[1], k - 0.38, q[2], k - 0.38, lwd = 3, col = pal[k])
  }
  text(truth, length(draws) + 0.55, "true value", pos = 4, col = ink, cex = 0.85)
}
```

```{r, fig.alt = "Bootstrap replicates of the coefficient of x2 for one data set. With leave-one-out nearly all replicates are exactly zero; without, they spread across zero and the 90% interval reaches the true value."}
set.seed(11)
repeat {
  d <- make_data()
  b2 <- cov(d$x[, 2], d$y) / var(d$x[, 2])
  if (sign(b2) != sign(beta[2])) break
}
draws <- list(boot_coefs(d, loo = TRUE)[2, ], boot_coefs(d, loo = FALSE)[2, ])
replicate_plot(draws, beta[2], c("loo = TRUE", "loo = FALSE"),
               "x2 with the wrong univariate sign")
sapply(draws, function(v) c(at_zero = mean(v == 0), quantile(v, c(0.05, 0.95))))
```

## What this means for inference

The leave-one-out uniReg is a shrinkage estimator. Its shrinkage, $2\sigma^2/(S_j |b_j|)$
in the orthogonal case, is of the order of the standard error, so its sampling
distribution is not centered at the true coefficient, and the percentile bootstrap
inherits that bias. Without leave-one-out, the bias disappears. The percentile bootstrap
then does reasonably in these simulations, but it has no guarantee near the boundary
that the sign constraints create.

The selective intervals of `unilasso_inference()` take another route. They condition on
the selection and on the signs, and they estimate the full-model coefficient by least
squares, without the constraint and without shrinkage. That makes them exact in the
Gaussian linear model for `loo = FALSE` fits. `unilasso_inference()` also accepts
`loo = TRUE` fits, which solve the `loo = FALSE` problem at the shifted penalties
$(n\lambda + \kappa_j)/|b_j|$. That inference is approximate, but close to calibrated;
see `vignette("unilasso_loo")`.

## Reference

Chatterjee, S., Hastie, T. and Tibshirani, R. (2025). Univariate-guided sparse regression.
*arXiv preprint*. doi:10.48550/arXiv.2501.18360
